Tree establishment in models of forest dynamics: a key priority for further research

### 2023-04-26 manuscript/manuscriptRW.Rmd
added authors and corrected accents in surnames

---
title: "Tree establishment in models of forest dynamics: a key priority for further research"
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Kristin H. Braziunas,
- Josef	Bruna,
- Samuel Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Katarina Merganicova,
- Tobias Mette,
- Xavier Morin,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

```{r tableModels, echo=FALSE,  message=FALSE, warning=FALSE}
library(knitr)

modelDF <- readr::read_csv(here::here("data", "modelsDescription.csv"))
modelDF$Sampling <- NULL

>>>>

---
title: "Tree establishment in models of forest dynamics: a key priority for further research"
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
---

@@

```{r tableModels, echo=FALSE,  message=FALSE, warning=TRUE}
library(knitr)
modelDF <- readr::read_csv(here::here("data", "modelsDescription.csv"))
modelDF$Sampling <- NULL
